%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} \\
      {\small#4}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeWorkExStart}[3]{
  \begin{itemize}[leftmargin=0.15in, label={}]%
  \item \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}%
    \textbf{#1} & \textit{\small{#2}}%
  \end{tabular*}%
  \vspace{-3pt}\item \textit{#3}%
  % \vspace{-3pt}\item \textbf{Responsibilities:}%
  \begin{itemize}%
}
\newcommand{\resumeWorkExEnd}{\end{itemize}\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Nguyen Van Tuong} \\ \vspace{10pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:84824967943}{+84 824 967 943}
    $|$
    \faAt \hspace{.5pt} \href{mailto:tuongnv99@gmail.com}{tuongnv99@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/tuongnv}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/tuongnv99}{GitHub}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://maps.app.goo.gl/7cBHvJBrCku3NF1v7}{Me Tri, Hanoi}
\end{center}



%----------- SUMMARY -----------
\section{Summary}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \hspace{10pt}
        { Results-driven Backend Developer with 3+ years of experience in developing and deploying web applications, databases, and APIs. Expert in designing, optimizing, and troubleshooting backend systems to ensure maximum performance and reliability. Adept at creating secure, scalable, and efficient code.}
    }}
  \resumeSubHeadingListEnd



%----------- SKILLS -----------
\section{Skills}
  \vspace{3pt}
  \small
    \begin{minipage}[t]{0.5\textwidth}
    \begin{enumerate}[label=•]
      \item \textbf{Programming Languages:}
      \begin{itemize}[label=-, topsep=-1.5pt]
        \item PHP, JavaScript, Java
        \item HTML5, CSS3
      \end{itemize}
      \item \textbf{Database Management Systems:}
      \begin{itemize}[label=-, topsep=-1.5pt]
        \item MySQL, PostgreSQL
        \item MongoDB, Redis
      \end{itemize}
      \item \textbf{Soft Skills:}
      \begin{itemize}[label=-, topsep=-1.5pt]
        \item Problem-solving, communication
        \item Continuous learning, adaptability
      \end{itemize}
    \end{enumerate}
    \end{minipage}%
    \hfill
    \begin{minipage}[t]{0.5\textwidth}
    \begin{enumerate}[label=•]
      \item \textbf{Frameworks/Platforms:}
      \begin{itemize}[label=-, topsep=-1.5pt]
        \item Magento, Laravel
        \item Serverless Lambda AWS
        \item Spring Boot
        \item jQuery, Bootstrap
      \end{itemize}
      \item \textbf{DevOps Tools:}
      \begin{itemize}[label=-, topsep=-1.5pt]
        \item Manage Version Control with Git
        \item Containerization with Docker
        \item CI/CD Pipelines with Jenkins, GitLab CI/CD
      \end{itemize}
    \end{enumerate}
    \end{minipage}%

    \begin{enumerate}[label=•]
      \item \textbf{Other:}
      \begin{itemize}[label=-, topsep=-1.5pt]
        \item Understanding web app security, including authentication and authorization.
        \item Implementing caching for database and application performance.
        \item Writing unit tests and debugging for code reliability.
        \item Deployment and management using cloud platforms (AWS) and Kubernetes
      \end{itemize}
    \end{enumerate}

%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {Hanoi University of Industry}
      {Compeleted in 2020}
      {Software Engineering}
      {Bachelor's Degree of Engineer}
  \resumeSubHeadingListEnd



%----------- WORK	EXPERIENCE -----------
\section{Work Experience}
  \resumeWorkExStart{Mageplaza Co., Ltd}{01/2021 - 03/2022}{Magento Developer}
    \resumeItem{Understanding project and client requirements, followed by writing code to develop features and customize interfaces.}
    \resumeItem{Maintenance products and provide ongoing assistance to global customers.}
    \resumeItem{To ensure the website runs smoothly and quickly, thorough testing is conducted to identify and fix any issues.}
  \resumeWorkExEnd

  \resumeWorkExStart{Rikkeisoft Co., Ltd}{04/2022 - Present}{Backend Developer}
    \resumeItem{Understanding project requirements and client needs is the initial step, followed by writing code to develop features and customize interfaces.}
    \resumeItem{Maintenance products and provide ongoing assistance to global customers.}
    \resumeItem{To ensure the website runs smoothly and quickly, thorough testing is conducted to identify and fix any issues.}
  \resumeWorkExEnd

\end{document}
