%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  % \cventry
  %   {Backend Developer / Team Lead} % Job title
  %   {Rikkeisoft Co., Ltd} % Organization
  %   {Me Tri, Hanoi} % Location
  %   {Apr. 2022 - Present} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Led backend development for mid-to-large scale platforms including e-commerce, scheduling tools, and a Forex trading system.}
  %       \item {Collaborated with BAs to analyze requirements, estimate effort, and define development phases aligned with business goals.}
  %       \item {Designed and optimized MySQL schemas and queries, reducing average query latency by ~30\% and improving overall database efficiency.}
  %       \item {Managed a team of 4–6 developers: delegated tasks, reviewed PRs, maintained code quality, and ensured on-time delivery in Agile sprints.}
  %       \item {Built and maintained RESTful APIs; integrated with frontend teams and supported QA in testing and rapid bug resolution.}
  %       \item {Prepared detailed release documentation and deployment checklists to ensure safe, repeatable releases; deployed via Docker and CI/CD pipelines, and followed up with client feedback resolution.}
  %       \item {Mentored interns and fresher developers, designed onboarding/training roadmaps, and supported long-term team skill development.}
  %     \end{cvitems}
  %   }

  % \cventry
  %   {Backend Developer}
  %   {Rikkeisoft Co., Ltd}
  %   {Hanoi, Vietnam}
  %   {Apr. 2022 – Dec. 2023}
  %   {
  %     \begin{cvitems}
  %       \item {\textbf{Key technologies:} Laravel, PostgreSQL, Redis, Docker, CI/CD, VNPAY, GHN}
  %       \item Developed and maintained 40+ Laravel REST APIs for catalog, cart, checkout, and order modules.
  %       \item Designed and normalized PostgreSQL schemas; improved query performance with indexes and materialized views.
  %       \item Implemented Redis caching to reduce average response latency by 35\%.
  %       \item Integrated local payment gateways and shipping APIs via secure REST endpoints.
  %       \item Used Laravel queues and Horizon for background jobs (email, order processing).
  %       \item Dockerized services and configured CI/CD pipelines for staging/production.
  %     \end{cvitems}
  %   }

  \cventry
    {Backend Developer / Team Lead} % Job title
    {Rikkeisoft Co., Ltd} % Organization
    {Me Tri, Hanoi} % Location
    {Apr. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participated in backend development of multiple systems, including a Forex trading platform (as team lead), an e-commerce site, and an internal scheduling tool. Applied various tech stacks and design approaches.}
        \vspace{0.5em}
        % Project item
        \item[] \textbf{Forex Trading Platform} — Financial system supporting thousands of concurrent users
        \vspace{0.15em}
        \item[] \textbf{Tech stack:} Serverless (Node.js on AWS Lambda), MySQL, Docker, AWS Cloud services (SQS, SNS, API Gateway)
        \vspace{0.25em}
        \begin{itemize}[label=•,itemsep=0.15em]
          \item {Led backend development for the core operations system of a large-scale Forex platform.}
          \item {Worked with BAs on requirement analysis, estimation, and phased planning.}
          \item {Designed and optimized MySQL schemas; reduced query latency by ~30\%.}
          \item {Managed 4–6 developers; assigned tasks, reviewed PRs, and ensured sprint delivery.}
          \item {Built REST APIs, collaborated with frontend, QA, and handled bug fixes.}
          \item {Documented releases, created deployment checklists, and managed CI/CD with Docker.}
          \item {Mentored juniors; created onboarding guides and skill-building plans.}
        \end{itemize}
        \vspace{0.5em}
        % Project item
        \item[] \textbf{E-commerce Platform} — Online storefront with full shopping and payment flow
        \vspace{0.15em}
        \item[] \textbf{Tech stack:} PHP (Laravel), PostgreSQL, Redis, Docker, VNPAY, MoMo
        \vspace{0.25em}
        \begin{itemize}[label=•,itemsep=0.15em]
          \item {Developed RESTful APIs for catalog, cart, checkout, and order management}
          \item {Designed PostgreSQL schemas and leveraged materialized views for reporting}
          \item {Implemented Redis caching for product details and category listings}
          \item {Integrated payment gateways and shipping APIs via secure REST endpoints}
          \item {Used Laravel queues and Horizon for background jobs (email, order processing)}
          \item {Dockerized services and configured CI/CD pipelines for staging/production}
        \end{itemize}
        \vspace{0.5em}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Magento Developer} % Job title
    {Mageplaza Co., Ltd} % Organization
    {Ha Dong, Hanoi} % Location
    {Jan. 2021 - Mar. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained Magento 2 extensions to enhance e-commerce websites, supporting 1000+ global merchants.}
        \item {Built modules such as Product Feed, Reward Points, SEO Toolkit, and Extra Fee – focused on scalability, compatibility, and performance.}
        \item {Customized features based on client requests and provided technical support for installation, bug fixing, and integration.}
        \item {Wrote clean, reusable PHP code following Magento development standards; optimized SQL queries for high-traffic stores.}
        \item {Collaborated with frontend, QA, and support teams to deliver high-quality releases and reduce issue turnaround time.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
